S-Aligner: Ultrascalable read mapping on Sunway Taihu Light

### 2017-04-19 s-aligner.tex
git test
add the funding acknowledgments
added page number to pages

\title{S-Aligner: Ultrascalable read mapping on Sunway Taihu Light}

\author{\IEEEauthorblockN{Xiaohui Duan, Kai Xu, Yuandong Chan}
\IEEEauthorblockA{
Shandong University\\
Jinan, China\\
Email: \{sunrise.duan, xu\_kai, yuandong.c\}@mail.sdu.edu.cn}
\and
\IEEEauthorblockN{Christian Hundt, Bertil Schmidt}
\IEEEauthorblockA{Johannes Gutenberg University\\
Mainz, Germany\\
Email: \{hundt, bertil.schmidt\}@uni-mainz.de}
\and
\IEEEauthorblockN{Pavan Balaji}
\IEEEauthorblockA{Argonne National Laboratory\\
Lemont, Illinois, USA\\
Email: balaji@anl.gov}
\and
\IEEEauthorblockN{Weiguo Liu}
\IEEEauthorblockA{Shandong University\\
Jinan, China\\
Email: weiguo.liu@sdu.edu.cn\\
}
}

@@

\section*{Acknowledgment}
This material is based upon work supported by the U.S. Department of
Energy, Office of Science, under contract DE-AC02-06CH11357.

>>>>

\title{S-Aligner: Ultrascalable read mapping on Sunway Taihu Light}
\thispagestyle{plain}
\pagestyle{plain}
\author{\IEEEauthorblockN{Xiaohui Duan, Kai Xu, Yuandong Chan}
\IEEEauthorblockA{
Shandong University\\
Jinan, China\\
Email: \{sunrise.duan, xu\_kai, yuandong.c\}@mail.sdu.edu.cn}
\and
\IEEEauthorblockN{Christian Hundt, Bertil Schmidt}
\IEEEauthorblockA{Johannes Gutenberg University\\
Mainz, Germany\\
Email: \{hundt, bertil.schmidt\}@uni-mainz.de}
\and
\IEEEauthorblockN{Pavan Balaji}
\IEEEauthorblockA{Argonne National Laboratory\\
Lemont, Illinois, USA\\
Email: balaji@anl.gov}
\and
\IEEEauthorblockN{Weiguo Liu}
\IEEEauthorblockA{Shandong University\\
Jinan, China\\
Email: weiguo.liu@sdu.edu.cn}
}

@@

\section*{Acknowledgment}
This material is based upon work supported by the PPP project from CSC and DAAD, 
Taishan Scholar, and the U.S. Department of Energy, Office of Science, under contract 
DE-AC02-06CH11357.
